CUDA-accelerated genetic feedforward-ANN training for data mining

### 2010-07-09 doc/HPCS-proceedings-paper.tex
Formatted the tables and figures
git-svn-id: http://svn.scesoc.ca/evolution/trunk@124 fee98b4c-d1c3-4d34-9525-a468159e4a48

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ann-chromosome}
	\caption{ANN structure and related chromosome design.  Each element in the chromosome is a real-valued number.}
	\label{fig:ann-chromosome}
\end{figure}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{lllll}
	\textbf{Legend Label} & \textbf{Hardware} & \textbf{Clock} & \textbf{Free RAM} & \textbf{OS} \\
	\hline
	x86    & x86 Desktop Processor  & 2.66~GHz & 7.5~GB & Linux 2.6 (64-bit) \\
	GTX260 & NVidia GTX260 GPU      & 1.24~GHz & N/A    & Windows 7 (64-bit) \\
	GTX275 & NVidia GTX275 GPU      & 1.4~GHz  & N/A    & Linux 2.6 (64-bit) \\
	\hline
	\end{tabular}
	\caption{Experimental hardware. Free RAM is OS-reported available memory before running each experiment.}
	\label{tab:experimental-hardware}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{fig-performance-genericx86}
	\caption{Training performance as a function of population size (left) and training set size (right). Note logarithmic axes.}
	\label{fig:training-performance}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{fig-evolution-lift}
	\caption{Evolution of classifier lift. Note logarithmic generation number axis.}
	\label{fig:evolution-lift}
\end{figure}

>>>>

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{ann-chromosome}
	\caption{\label{fig:ann-chromosome}ANN structure and related chromosome design.  Each element in the chromosome is a real-valued number.}
	\end{center}
\end{figure}

@@

\begin{table}[h]
	\caption{\label{tab:experimental-hardware}Experimental hardware. Free RAM is OS-reported available memory before running each experiment.}
	\begin{center}
	\begin{tabular}{lllll}
	\br
	Legend Label&Hardware&Clock&Free RAM&OS\\
	\mr
	x86   &x86 Desktop Processor&2.66~GHz&7.5~GB&Linux 2.6 (64-bit) \\
	GTX260&NVidia GTX260 GPU    &1.24~GHz&N/A   &Windows 7 (64-bit) \\
	GTX275&NVidia GTX275 GPU    &1.4~GHz &N/A   &Linux 2.6 (64-bit) \\
	\br
	\end{tabular}
	\end{center}
\end{table}

@@

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{fig-performance-genericx86}
	\caption{\label{fig:training-performance}Training performance as a function of population size (left) and training set size (right). Note logarithmic axes.}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.5\textwidth]{fig-evolution-lift}
	\caption{\label{fig:evolution-lift}Evolution of classifier lift. Note logarithmic generation number axis.}
	\end{center}
\end{figure}
